\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Updated Figure 6

### Algorithm to represent the model in 2D

@@

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  theme(
    legend.position = "bottom"
  )

error_plot_scurve 
```

>>>>

### Algorithm to represent the model in \gD{}

@@

error_plot_scurve <- error_df_scurve |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type)) +
  geom_point(alpha=0.5) +
  theme(
    legend.position = "bottom"
  )
```

```{r}
#| label: fig-p-d-error-in-2d-scurve
error_plot_scurve
```

### 2024-08-14 paper.tex
Added figure 10
Updated Figure 6

\subsection{Algorithm to represent the model in
2D}\label{algorithm-to-represent-the-model-in-2d}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/p-d-error-in-2d-scurve-1.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-23-1.pdf}
\end{center}

@@

\caption{\label{fig-five-gau-projs}(a) tSNE}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-54-1.pdf}
\end{center}

>>>>

\subsection{\texorpdfstring{Algorithm to represent the model in
\gD{}}{Algorithm to represent the model in }}\label{algorithm-to-represent-the-model-in}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-p-d-error-in-2d-scurve-1.pdf}

\caption{\label{fig-p-d-error-in-2d-scurve}}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-24-1.pdf}
\end{center}

@@

\caption{\label{fig-five-gau-projs}(a) tSNE, (b) UMAP, and (c) PaCMAP}

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-57-1.pdf}
\end{center}
